Funding programmes for early career researchers do/not influence their independence

### 2023-06-09 article.Rmd
small changes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
library(cobalt)
library(knitr)
library(psych)
library(kableExtra)
library(ggplot2)
```

@@

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
d$disc_ford <- as.factor(d$disc_ford)

@@

@@

ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         theme_bw()

@@

ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "disc_ford", y = "Mean RII") +
         theme_bw()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(tidyr)
library(dplyr)
library(cobalt)
library(knitr)
library(psych)
library(kableExtra)
library(ggplot2)
```

@@

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
d$disc_ford <- substring(d$disc_ford, 0, 1)
d$disc_ford <- as.factor(d$disc_ford)

@@

When Looking at disciplines, we see that there are slightly more missing data in the discipline group 1 (Natural Sciences).

dt <- d
dt$missing <- ifelse(is.na(dt$RII), "Missing", "Complete")

# Calculate counts and proportions
df_summary <- dt %>%
  group_by(disc_ford, missing) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(Proportion = count / sum(count)) %>%
  pivot_wider(names_from = missing, values_from = c(count, Proportion))

# Calculate Missing / (Missing + Complete) in percentages for each disc_ford
df_summary <- df_summary %>%
  mutate(Proportion = ifelse(!is.na(`count_Missing`) & !is.na(`count_Complete`), `count_Missing` / (`count_Missing` + `count_Complete`) * 100, NA))

# If there are any NA values in the 'Proportion' column, replace them with 0
df_summary[is.na(df_summary$Proportion)] <- 0

# Remove unnecessary columns and rename the others
df_summary <- df_summary %>%
  select(disc_ford, count_Complete, count_Missing, Proportion) %>%
  rename(
    Complete = count_Complete,
    Missing = count_Missing,
    Proportion_Missing = Proportion
  )

# Print the updated table
kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing data by disc_ford") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

ggplot(data = means_before_treatment, aes(x = treatment, y = RII, fill = treatment)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         scale_fill_discrete(name = "treatment") +
         theme_bw()

@@

ggplot(data = means_before_disc, aes(x = disc_ford, y = RII, fill = disc_ford)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "disc_ford", y = "Mean RII") +
         scale_fill_discrete(name = "disc_ford") +
         theme_bw()
